Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-05-16 Papers/ms.tex
end enumerate
Working title
MOre references

\title[]
{Lensing}

@@

In this paper we address the topic of
inferring the matter distribution in the lens galaxy from the lensed,
blurred image. These approaches may be categorized according to the following
criteria:
\begin{enumerate}
\item Whether to use a simply parameterized (e.g. Sérsic), moderately flexible
(e.g. mixture model, \citet{2011MNRAS.412.2521B})
or free-form (e.g. pixellated) model for the surface brightness profile of the source
\item Whether to use a simply parameterized (e.g. Singular Isothermal Ellipsoid)
or flexible model (e.g. pixellated) for the mass profile of the lens
\item How to compute the results (e.g. optimization methods, Markov Chain

Many different approaches have been proposed and applied to
this problem. The differences between the approaches can be broken down into
i) different assumptions about the prior information being used, and ii)
different computational methods used to compute the results.
Each approach involves tradeoffs between convenience and realism.
Simply parameterized models, such as Sérsic surface
brightness profiles for the source, and SIE models for the lens, are very
convenient. They only have a few adjustable parameters, and they capture
(to ``first order'') relevant prior information that we have about the
source and lens profiles. Of course, they are clearly simplifications,
and can produce misleading results if the actual profile is very different
from any member of the assumed family.

@@

Computing the posterior distribution over the parameters of such a model
requires that we can implement Markov Chain Monte Carlo (MCMC) over the space
of possible sources and lenses. In a recent paper,

@@

@@

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay,
\& Cs{\'a}nyi}{2011}]{dnest} Brewer B.~J., P{\'a}rtay L.~B., Cs{\'a}nyi G., 2011,
Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380

@@

@@

@@

>>>>

\title[]
{Trans-Dimensional Inference for Gravitational Lens Substructures}

@@

In this paper we address the topic of
inferring the matter distribution in the lens galaxy from the lensed,
blurred image. These approaches may be categorized according to the following
criteria:
\begin{enumerate}
\item Whether to use a simply parameterized (e.g. Sérsic), moderately flexible
(e.g. mixture model, \citet{2011MNRAS.412.2521B})
or free-form (e.g. pixellated) model for the surface brightness profile of the source
\item Whether to use a simply parameterized (e.g. Singular Isothermal Ellipsoid)
or flexible model (e.g. pixellated) for the mass profile of the lens
\item How to compute the results (e.g. optimization methods, Markov Chain
Monte Carlo with or without source parameters marginalized out).
\end{enumerate}

Many different approaches have been proposed and applied to
this problem. Recent sophisicated approaches to
this problem include \citet{2014MNRAS.445.2181C},
\citet{2015arXiv150500198T}, and
\citet{2015arXiv150407629B}. {\bf todo: actually comment
on what's in these papers}.

The differences between the approaches can be broken down into
i) different assumptions about the prior information being used, and ii)
different computational methods used to compute the results.
Each approach involves tradeoffs between convenience and realism.
Simply parameterized models, such as Sérsic surface
brightness profiles for the source, and SIE models for the lens, are very
convenient. They only have a few adjustable parameters, and they capture
(to ``first order'') relevant prior information that we have about the
source and lens profiles. Of course, they are clearly simplifications,
and can produce misleading results if the actual profile is very different
from any member of the assumed family.

@@

Computing the posterior distribution over the parameters of such a model
requires that we can implement Markov Chain Monte Carlo (MCMC) over the space
of possible sources and lenses.

@@

Since the model is not of fixed dimension (the number of source and lens
``blobs'' is unknown), we implemented the MCMC using the {\tt RJObject}
\citep{rjobject} software, a C++ library for implementing trans-dimensional
MCMC with hierarchically-specified priors, and doing the sampling with the
Diffusive Nested Sampling algorithm \citep{dnest}. Previous astronomical
applications of {\tt RJObject} include \citet{magnetron}
and~\ref{exoplanet}.

@@

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Birrer, Amara, 
\& Refregier}{2015}]{2015arXiv150407629B} Birrer S., Amara A., Refregier A., 2015, arXiv, arXiv:1504.07629

\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay,
\& Cs{\'a}nyi}{2011}]{dnest} Brewer B.~J., P{\'a}rtay L.~B., Cs{\'a}nyi G., 2011,
Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380

@@

\bibitem[\protect\citeauthoryear{Brewer 
\& Donovan}{2015}]{exoplanet} Brewer B.~J., Donovan C.~P., 2015, MNRAS, 448, 3206

@@

\bibitem[\protect\citeauthoryear{Huppenkothen et 
al.}{2015}]{magnetron} Huppenkothen D., et al., 2015, arXiv, 
arXiv:1501.05251

@@

\bibitem[\protect\citeauthoryear{Tagore 
\& Jackson}{2015}]{2015arXiv150500198T} Tagore A.~S., Jackson N., 2015, arXiv, arXiv:1505.00198
